---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timemoir

<!-- badges: start -->
[![R-CMD-check](https://github.com/nbc/timemoir/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/nbc/timemoir/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/nbc/timemoir/branch/main/graph/badge.svg)](https://app.codecov.io/gh/nbc/timemoir?branch=main)
<!-- badges: end -->

## Overview

The goal of timemoir is to benchmark the memory usage, CPU usage, and execution time of functions that cannot be accurately profiled using traditional benchmarking tools. It is particularly useful for profiling **long-running or memory-intensive operations**, such as those involving in-memory analytics with `arrow` or `duckdb`.

Unlike traditional profilers like `Rprof()` or `profmem`, `timemoir` uses a **forked R process** to run each function in isolation, while the parent process monitors memory consumption via [`ps::ps_memory_info()`](https://ps.r-lib.org/) and  `proc.time()`. 

It's a simple but effective approach.

## Features:

- Memory Profiling: Tracks initial and peak memory usage (`start_mem`, `max_mem`)
- CPU Usage: Measures user and system CPU time
- Elapsed Time: Captures real execution time (`proc.time`)
- Error Handling: Catches and reports errors without stopping the benchmarking loop
- Repetition: Supports repeated benchmarking with `n` runs per function

> ❗ **Note**: This package works only on **Unix**.
> It relies on parallel package to fork a process.

## Installation

To install the package, run the following command in your R console:

```{r, eval=FALSE}
devtools::install_github("nbc/timemoir")
```

## Example

```{r example}
library(timemoir)
library(ggplot2)

test_function <- function(n) {
  x <- rnorm(n)
  mean(x)
}

res <- timemoir(
  test_function(1.2e7),
  test_function(1.5e7), 
  test_function(1e7)
)
res

autoplot(res)
```

## Why use `timemoir`?

Benchmarking tools like `bench::mark()` or `microbenchmark()` are powerful for **fast** functions. But if you're dealing with:

- Queries that stream data from disk,
- `duckdb::dbGetQuery()` on large tables,
- `arrow::open_dataset()` and lazy evaluations,
- or R functions with unpredictable memory usage,

...then `timemoir` gives you visibility into what’s really happening — in memory, CPU and in time.

