---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timemoir

<!-- badges: start -->
[![R-CMD-check](https://github.com/nbc/timemoir/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/nbc/timemoir/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `timemoir` is to get memory usage of large functions doing many things
(like `duckdb` or `arrow` calculations). `utils::Rprof` and `profmem` don't work
well for this use case.

To achieve this goal, the `timemoir` fork an R processus that execute the
function while the main processus read memory usage in `/proc/<pid>/status`.

This is a bit crude but works well for me.

As this package reads `/proc/<pid>/status`, it doesn't work on windows.

## Installation

You can install the development version of timemoir like so:

```{r, eval=FALSE}
devtools::install_github("nbc/timemoir")
```

## Example

```{r example}
library(timemoir)

timemoir(Sys.sleep(1), Sys.sleep(2), Sys.sleep())
```

