---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timemoir

<!-- badges: start -->
[![R-CMD-check](https://github.com/nbc/timemoir/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/nbc/timemoir/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/nbc/timemoir/branch/main/graph/badge.svg)](https://app.codecov.io/gh/nbc/timemoir?branch=main)
<!-- badges: end -->

## Overview

This package offers a low level framework for benchmarking the memory usage and
execution time of R functions. It is designed to assist developers and analysts
in profiling and optimizing the performance of their code, particularly for
long-running functions or processes that rely heavily on disk I/O or in memory
database queries like `arrow` and `duckdb` that can not be benchmark by classic
methods.

Key Features:

- **Detailed Profiling**: Measures the memory usage and execution time of functions, providing insights into their performance.
- **Error Reporting**: Captures errors during execution to aid debugging and improve reliability.

To achieve its goal, `timemoir` fork an R process that executes the
function, while the main process read memory usage in `/proc/<pid>/status`.
Althoug a bit crude this approach is effective.

It's a simple but effective approach.

> ❗ **Note**: This package works only on **Linux**.  
> It relies on the `/proc/<pid>/status` filesystem to track memory usage.

## Installation

To install the package, run the following command in your R console:

```{r, eval=FALSE}
devtools::install_github("nbc/timemoir")
```

## Example

```{r example}
library(timemoir)

test_function <- function(n) {
  x <- rnorm(n); mean(x)
}

timemoir(
  test_function(1e3),
  test_function(1e6),
  test_function(1e8)
)
```

